Simulation Explorer

### 2018-05-17 inst/rmd/vis_sim.Rmd
Minor clean-up during review

```{r}
e$d <- as.data.frame.table(e$sim$N, responseName = "N")
names(e$d) <- c("Age", "Year", "N")
e$d$text <- paste0("Age: ", e$d$Age, "\nYear: ", e$d$Year, "\nN: ", round(e$d$N))
plot_ly(x = ~Age, y = ~Year, z = ~N, color = ~Age,
        text = ~text, hoverinfo = "text",
        colors = viridis(length(e$ages)),
        type = "scatter3d", mode = "lines",
        line = list(width = 8),
        data = e$d)
```

>>>>

plot_ly(x = e$ages, y = e$years, z = e$sim$N, type = "surface") %>% 
  layout(
    scene = list(
      xaxis = list(title = "Age"),
      yaxis = list(title = "Year"),
      zaxis = list(title = "N")
    ))
